Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-05 paper/ms.tex
Clean up preamble; add affiliations

% to-do list
% ----------
% - Add references and uncertainties to Table 1

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

\include{gitstuff}
\include{aastexmods}

@@

\title{Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair}

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  APW, JMB, KH, NL, DWH, DNS \etal\
}

% Affiliations
\newcommand{\pu}{1}
\newcommand{\lead}{2}
\newcommand{\ccpp}{3}
\newcommand{\mpia}{4}
\newcommand{\cca}{5}

\altaffiltext{\pu}{Department of Astrophysical Sciences,
                   Princeton University, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
                     \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
                     Department of Physics,
                     New York University, 4 Washington Place,
                     New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
                     K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Center for Computational Astrophysics, 162 5th Ave, New York, NY 10003, USA}

>>>>

% to-do list
% ----------
% - Add items here.

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.
% - Use "comoving" instead of "co-moving".
% - Write elements as \elem{X}.

\include{aastexmods}

@@

\title{
  Kronos \& Krios:
  Evidence for accretion of massive, rocky planetary system in a sun-like pair
}

\author{
  Semyeong Oh\altaffilmark{\pu,\lead},
  Adrian M. Price-Whelan\altaffilmark{\pu},
  John M. Brewer\altaffilmark{\yale},
  Keith A. Hawkins\altaffilmark{\columbia},
  Nathan W. C. Leigh\altaffilmark{\amnh},
  David W. Hogg\altaffilmark{\ccpp,\mpia,\cca},
  David N. Spergel\altaffilmark{\pu,\cca},
  Justin Myles\altaffilmark{\yale} \etal\
}

% Affiliations
\newcommand{\pu}{1}
\newcommand{\lead}{2}
\newcommand{\yale}{3}
\newcommand{\columbia}{4}
\newcommand{\amnh}{5}
\newcommand{\ccpp}{6}
\newcommand{\mpia}{7}
\newcommand{\cca}{8}

\altaffiltext{\pu}{Department of Astrophysical Sciences,
  Princeton University, 4 Ivy Ln, Princeton, NJ 08544, USA}
\altaffiltext{\lead}{To whom correspondence should be addressed:
  \texttt{semyeong@astro.princeton.edu}}
\altaffiltext{\columbia}{Department of Astronomy,
  Columbia University, 550 W 120th St, New York, NY 10027, USA}
\altaffiltext{\yale}{Department of Astronomy,
  Yale University, 260 Whitney Ave, New Haven, CT 06511, USA}
\altaffiltext{\amnh}{Department of Astrophysics,
  American Museum of Natural History, Central Park West and 79th St, New York, NY 10024, USA}
\altaffiltext{\ccpp}{Center for Cosmology and Particle Physics,
  Department of Physics,
  New York University, 4 Washington Place,
  New York, NY 10003, USA}
\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
  K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cca}{Center for Computational Astrophysics,
  Flatiron Institute, 162 5th Ave, New York, NY 10003, USA}
